### 2022-03-01 paper/localpsf.tex
moved old stuff to end. rearranging sections

\subsubsection{Estimating impulse response supports}
\label{eq:mean_and_covariance_estimation}

Because of the non-negative kernel property, for each $x \in \Omega$, the impulse response $\impulseresponse_x$ is a non-negative function $y \mapsto \impulseresponse_x(y)$. Hence, $\impulseresponse_x$ is a scaled probability distribution. Let $\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy$ denote the scaling factor (the ``volume'' of $\impulseresponse_x$), let $\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)$ denote the normalized version of $\impulseresponse_x$, and let $\spatialmean(x)$ and $\spatialcov(x)$ denote the mean and covariance of $\widehat{\impulseresponse}_x$, respectively. We make the approximation that the support of $\impulseresponse_x$ is contained within the ellipsoid
\begin{equation}
	\label{eq:support_ellipsoid}
	E_x := \{x' \in \Omega: (x' - \spatialmean(x))^T \spatialcov(x)^{-1} (x' - \spatialmean(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a fixed constant. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations from the mean of the Gaussian distribution with mean $\spatialmean(x)$ and covariance $\spatialcov(x)$, i.e., the Gaussian distribution which has the same mean and covariance as $\widehat{\impulseresponse}_x$ (see Figure FIG). The quantity $\tau$ is a parameter that must be chosen by the user of the algorithm. The larger $\tau$ is, the larger the ellipsoid $E_x$ is, and the more conservative the estimate is for the support of $\impulseresponse_x$. However, the cost of our algorithm will depend on how many non-overlapping ellipsoids $E_x$ we can ``pack'' in the domain $\Omega$ (more ellipsoids $\implies$ lower cost), and choosing a larger value of $\tau$ means that fewer ellipsoids will fit in $\Omega$. We find that $\tau=3$ yields a reasonable balance between these competing interests, and use $\tau=3$ in our numerical results. The fraction of the ``mass'' of $\impulseresponse_x$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though this bound is conservative and typically far less mass resides in this region.

@@

\subsection{Convolution kernels}
\label{sec:get_impulse_response}

@@

\subsection{Approximating kernel entries $\Phi(y,x)$}

@@

\subsubsection{Improvements when $\Aop$ is symmetric}
If $\Aop$ is symmetric, impulse responses of $\Aop$ are also impulse responses of $\Aop^T$. Let $\{y_i\}_{i=1}^k$ be the $k$ nearest sample points to $y$, excluding points $y_i$ such that $x - \mu(y) + \mu(y_i) \notin \Omega$. We could form an alternative approximation of $\Phi(y,x)$ by interpolating the (point, value) pairs
\begin{equation}
\label{eq:phi_mu_shift_y}
\left(y_i,f_{x,y}(y_i)\right), \qquad i=1,\dots,k,
\end{equation}
in the same manner as before, but with $x$ and $y$ now taking opposite roles. We improve the interpolation accuracy at negligible additional cost by combining both of these approximations. Specifically, we combine both approximations by placing function values 
\begin{equation*}
\left(\widetilde{f}_x\right)_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $x_i-x$, placing function values
\begin{equation*}
\left(\widetilde{f}_y\right)_i := \frac{V(y)}{V(y_i)}\phi_{y_i}\left(x - \mu(y) + \mu(y_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $y_i-y$, and interpolating the combination of all $2k$ of these points and values at zero.

>>>>

\subsubsection{Impulse response moments and support estimation}
\label{eq:mean_and_covariance_estimation}

Because of the non-negative impulse response property, for each $x \in \Omega$, the impulse response $\impulseresponse_x$ is a non-negative function $y \mapsto \impulseresponse_x(y)$. Hence, $\impulseresponse_x$ is a scaled probability distribution. Let $\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy$ denote the scaling factor (the ``volume'' of $\impulseresponse_x$), let $\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)$ denote the normalized version of $\impulseresponse_x$, and let $\spatialmean(x)$ and $\spatialcov(x)$ denote the mean and covariance of $\widehat{\impulseresponse}_x$, respectively. We make the approximation that the support of $\impulseresponse_x$ is contained within the ellipsoid
\begin{equation}
	\label{eq:support_ellipsoid}
	E_x := \{x' \in \Omega: (x' - \spatialmean(x))^T \spatialcov(x)^{-1} (x' - \spatialmean(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a fixed constant. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations from the mean of the Gaussian distribution with mean $\spatialmean(x)$ and covariance $\spatialcov(x)$, i.e., the Gaussian distribution which has the same mean and covariance as $\widehat{\impulseresponse}_x$ (see Figure FIG). The quantity $\tau$ is a parameter that must be chosen by the user of the algorithm. The larger $\tau$ is, the larger the ellipsoid $E_x$ is, and the more conservative the estimate is for the support of $\impulseresponse_x$. However, the cost of our algorithm will depend on how many non-overlapping ellipsoids $E_x$ we can ``pack'' in the domain $\Omega$ (more ellipsoids $\implies$ lower cost), and choosing a larger value of $\tau$ means that fewer ellipsoids will fit in $\Omega$. We find that $\tau=3$ yields a reasonable balance between these competing interests, and use $\tau=3$ in our numerical results. The fraction of the ``mass'' of $\impulseresponse_x$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though this bound is conservative and typically far less mass resides in this region.

@@

\subsection{Impulse response batches}
\label{sec:get_impulse_response}

@@

\subsection{Approximate integral kernel entries}

@@

\subsubsection{Improvements based on symmetry}
If $\Aop$ is symmetric, impulse responses of $\Aop$ are also impulse responses of $\Aop^T$. Let $\{y_i\}_{i=1}^k$ be the $k$ nearest sample points to $y$, excluding points $y_i$ such that $x - \mu(y) + \mu(y_i) \notin \Omega$. We could form an alternative approximation of $\Phi(y,x)$ by interpolating the (point, value) pairs
\begin{equation}
\label{eq:phi_mu_shift_y}
\left(y_i,f_{x,y}(y_i)\right), \qquad i=1,\dots,k,
\end{equation}
in the same manner as before, but with $x$ and $y$ now taking opposite roles. We improve the interpolation accuracy at negligible additional cost by combining both of these approximations. Specifically, we combine both approximations by placing function values 
\begin{equation*}
\left(\widetilde{f}_x\right)_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $x_i-x$, placing function values
\begin{equation*}
\left(\widetilde{f}_y\right)_i := \frac{V(y)}{V(y_i)}\phi_{y_i}\left(x - \mu(y) + \mu(y_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $y_i-y$, and interpolating the combination of all $2k$ of these points and values at zero.
